|

### 2019-09-05 paper.Rmd
working through tour section

The basis underlying our approach is the grand tour. We first briefly review the relevant concepts. Building on these ideas we then introduce a method for displaying slices of parameter space that are defined for each projection matrix.

@@

A tour is providing a continuous animation, showing a sequence of $d$-dimensional (typically $d=1$ or $2$) projections from $p$-dimensional parameter space. The tour combines basis selection with basis interpolation. In a grand tour the basis selection is random (each new basis is chosen from all possible projections), and typically geodesic interpolation is used to generate smooth transitions between viewing planes. Different basis selection methods as well as the geodesic interpolation are implemented in the `tourr` package [@tourr], which also provides several display functions for viewing the tour.

The notation used in the following for the description of each projection is denoting $\mathbf{X}$ the $n\times p$ dimensional data matrix ($n$ observations in $p$ dimensions) and $\mathbf{A}$ an orthonormal $p \times d$ projection matrix. The $d$-dimensional projection of the data is thus given by $\mathbf{Y} = \mathbf{X}\cdot\mathbf{A}$, giving the $n\times d$ dimensional projected data matrix to be plotted in each frame of the tour display.

>>>>

The sectioning is combined with the projections provided by a grand tour. A brief explanation of the tour is provided followed by an explanation of how slicing is done.

@@

A tour provides a continuous sequence of $d$-dimensional (typically $d=1$ or $2$) projections from $p$-dimensional Euclidean space. It is constructed by combining a method for basis selection with geodesic interpolation between pairs of bases. In a grand tour, the basis selection is random, each new basis is chosen from all possible projections. In a guided tour, the bases are chosen based on an index of interestingness. Different basis selection methods as well as the geodesic interpolation are implemented in the `tourr` package [@tourr], which also provides several display functions for viewing the tour.

For the explanation of the slice tour, the actual mechanics of the tour are not important, and only the notion of a projection plane in high dimensions is needed. The notation used for explanations starts with deoting each projection as $\mathbf{X}$ the $n\times p$ dimensional data matrix ($n$ observations in $p$ dimensions) and $\mathbf{A}$ an orthonormal $p \times d$ projection matrix. The $d$-dimensional projection of the data is thus given by $\mathbf{Y} = \mathbf{X}\cdot\mathbf{A}$, giving the $n\times d$ dimensional projected data matrix to be plotted in each frame of the tour display.
